My title

### 2024-12-03 paper/paper.qmd
reorganized data section

---
title: "My title"
subtitle: "My subtitle if needed"
author: Cher Ning-Li
thanks: "Code and data are available at: [https://github.com/cher-ning/cndgrocers)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(arrow)
library(here)
library(ggplot2)
library(modelsummary)
library(rstanarm)
library(knitr)

@@

After combining the two tables, `raw` and `product`, by matching each entry's unique product ID, the full dataset with $12,753,964$ entries was created. Then, entries with "egg" or "eggs", and "dozen" or "12" appearing in their product name or units were selected for. The `nowtime` variable, which tracks the time when the data was scraped, was generalized to a `month` variable for ease of analysis. All February entries were omitted from analysis due to data collection starting on 28 February, 2024, which means there is a lack of sufficient data for that month to make any reliable conclusions from. Then, calculation for each month's average `current_price` was done and added to each listing of the following month as the variable `prev_month_avg`.

The relevant variables, as listed and explained in the table below [@tbl-varoverview], was selected for and entries with empty entries in any of these key variables were dropped. It is important to note that this would filter out any unadvertised price changes, as only price decreases for an explicitly advertised sale event would include both `current_price` and `old_price`.

```{r}
#| label: tbl-varoverview
#| tbl-cap: Selected Variables Overview
#| echo: false
#| warning: false
#| message: false

columns <- data.frame(
  Column = c("month", "vendor", "current_price", "old_price", "product_name", "prev_month_avg"),
  Description = c(
    "Month of when the data was collected",
    "One of the 8 Canadian grocery vendors",
    "Price at time of extract",
    "An 'old' struck-out price, indicating the item's regular pre-sale price",
    "Product name, may include brand and/or units",
    "Average curren_price of a dozen eggs across all vendors, during the month before the data collection"
  )
)

kable(columns, caption = NULL)

@@

A snapshot of a couple entries from this cleaned dataset can be found in @sec-data-details.

@@

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

modelsummary::modelsummary(
  list(
    "First model" = model1
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: Cher Ning-Li
thanks: "Code and data are available at: (https://github.com/cher-ning/cndgrocers)[https://github.com/cher-ning/cndgrocers]."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(arrow)
library(here)
library(ggplot2)
library(modelsummary)
library(rstanarm)
library(knitr)
library(kableExtra)

@@

After combining the two tables, `raw` and `product`, by matching each entry's product ID, the full dataset with $12,753,964$ entries was created. Then, entries with "egg" or "eggs", and "dozen" or "12" appearing in their product name or units were selected for. All February entries were omitted from analysis due to data collection starting on 28 February, 2024, which means there is a lack of sufficient data for that month to make any reliable conclusions from. The relevant variables of interest to us are: `nowtime`, `vendor`, `current_price`, `old_price`, and `product_name`, as explained below:

- **nowtime**: Date and time of when the data was collected
- **vendor**: One of the 8 Canadian grocery vendors
- **current_price**: Price at time of extract
- **old_price**: An 'old' struck-out price, indicating the item's regular pre-sale price
- **product_name**: Product name, may include brand and/or units

For ease of analysis, some additional variables were derived.

- **month**: The month of when a data entry was collected; extracted from `nowtime`
- **prev_month_avg**: The average price of a dozen eggs across all vendors during the previous month

All entries with empty values in any of these key variables were dropped. It is important to note that this would filter out any unannounced price changes, as only price decreases for an explicitly advertised sale event would include both `current_price` and `old_price` variables. The first 5 rows from the cleaned dataset along with these derived variables is shown in @fig-datahead.

```{r}
#| label: fig-datahead
#| fig-cap: Sample of Analysis Data
#| fig-align: center
#| echo: false
#| warning: false
#| message: false

kable(head(analysis_data, 5)) %>% 
  kable_styling(
    font_size = 10,
    latex_options = c("scale_down"),
    full_width = FALSE,
    position = "center"
  ) %>% 
  column_spec(4, width = "15em")

@@

@@

#analysis_data |> 
#  ggplot(aes(x = width, y = length)) +
#  geom_point(alpha = 0.8) +
#  theme_minimal() +
#  labs(x = "Wing width (mm)",
#       y = "Wing length (mm)")
```

@@

#modelsummary::modelsummary(
#  list(
#    "First model" = model1
#  ),
#  statistic = "mad",
#  fmt = 2
#)
```

@@

plot(model1, "trace")

plot(model1, "rhat")
```
